Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-29 doc/RMD/by-year.Rmd
update some figures for results

```{r packages}
library("poppr")
library("tidyverse")
library("cowplot")
make_amova_table <- function(am, amt, samples = "Region"){
  tot <- nrow(am$results)
  res <- data.frame(list(am$results[-tot, c("Df", "Sum Sq")], 
                         Percent = am$componentsofcovariance[-tot, 2],
                         Pval    = rev(amt$pvalue), 
                         Phi     = rev(am$statphi$Phi[-tot])))
  res <- as.matrix(res)
  colnames(res) <- c("d.f.", "Sum of Squares", "Percent variation", "P", 
                     "Phi statistic")
  names(dimnames(res)) <- c("levels", "statistic")
  rownames(res) <- gsub("samples", samples, rownames(res))
  return(res)
}

@@

```{r AMOVA_table, comment = NA}
make_amova_table(full.amova.3, full.amova.3.test, samples = "Year") %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Region", "Between Source within Region", "Between Year within Source", "Within Year"), .before = 1) %>%
  readr::write_csv(path = file.path(PROJHOME, "results", "tables", "AMOVA-year.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate_if(is.numeric, format, digits = 3) %>%
  # mutate(ps = signif(ps, digits = 3)) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  # mutate(ps = case_when(P > 0.05 ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi$ statistic` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  rename(`*P*` = P) %>%
  select(c(1:4, 6, 5)) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(0.8, 0.15, 0.15, 0.35, 0.5, 0.15)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>% 
  huxtable::set_number_format(huxtable::everywhere, 2, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 6, 3) %>%
  huxtable::set_number_format(huxtable::everywhere, 5, 4) %>%
  huxtable::print_md(max_width = 80)
```

>>>>

```{r packages}
library("poppr")
library("tidyverse")
library("cowplot")
make_amova_table <- function(am, amt, samples = "Region"){
  tot <- nrow(am$results)
  res <- data.frame(list(am$results[-tot, c("Df", "Sum Sq")], 
                         Percent = am$componentsofcovariance[-tot, 2],
                         Pval    = rev(amt$pvalue), 
                         Sigma   = am$componentsofcovariance[-tot, 1],
                         Phi     = rev(am$statphi$Phi[-tot])))
  res <- as.matrix(res)
  colnames(res) <- c("d.f.", "Sum of Squares", "Percent variation", "P", 
                     "Phi statistic")
  names(dimnames(res)) <- c("levels", "statistic")
  rownames(res) <- gsub("samples", samples, rownames(res))
  return(res)
}

@@

```{r AMOVA_table, comment = NA}
make_amova_table(full.amova.3, full.amova.3.test, samples = "Year") %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Region", "Between Source within Region", "Between Year within Source", "Within Year"), .before = 1) %>%
  readr::write_csv(path = file.path(PROJHOME, "results", "tables", "AMOVA-year.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate_if(is.numeric, format, digits = 3) %>%
  # mutate(ps = signif(ps, digits = 3)) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  # mutate(ps = case_when(P > 0.05 ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi$ statistic` = ps) %>%
  rename(`$\\sigma^2$` = Sigma) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  rename(`*P*` = P) %>%
  select(c(1:3, 6, 4, 7, 5)) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(0.7, 0.1, 0.12, 0.27, 0.31, 0.42, 0.15)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:7, "right") %>% 
  huxtable::set_number_format(huxtable::everywhere, 2, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, c(4, 6), 3) %>%
  huxtable::set_number_format(huxtable::everywhere, 7, 4) %>%
  huxtable::print_md(max_width = 93)
```

### 2017-08-29 doc/RMD/wmn-differentiation.Rmd
update some figures for results

make_amova_table <- function(am, amt, samples = "Region"){
  tot <- nrow(am$results)
  res <- data.frame(list(am$results[-tot, c("Df", "Sum Sq")], 
                         Percent = am$componentsofcovariance[-tot, 2],
                         Pval    = rev(amt$pvalue), 
                         Phi     = rev(am$statphi$Phi[-tot])))
  res <- as.matrix(res)
  colnames(res) <- c("d.f.", "Sum of Squares", "Percent variation", "P", 
                     "Phi statistic")
  names(dimnames(res)) <- c("levels", "statistic")
  rownames(res) <- gsub("samples", samples, rownames(res))
  return(res)
}

>>>>

make_amova_table <- function(am, amt, samples = "Region"){
  tot <- nrow(am$results)
  res <- data.frame(list(am$results[-tot, c("Df", "Sum Sq")], 
                         Percent = am$componentsofcovariance[-tot, 2],
                         Pval    = rev(amt$pvalue), 
                         # Sigma   = rev(amt$)
                         Phi     = rev(am$statphi$Phi[-tot])))
  res <- as.matrix(res)
  colnames(res) <- c("d.f.", "Sum of Squares", "Percent variation", "P", 
                     "Phi statistic")
  names(dimnames(res)) <- c("levels", "statistic")
  rownames(res) <- gsub("samples", samples, rownames(res))
  return(res)
}

### 2017-08-29 doc/manuscript/manuscript.Rmd
update some figures for results

```{r table4, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
read_csv("../../results/tables/AMOVA-year.csv", 
         na = "NA", # spaces read in as spaces
         col_types = cols(.default = col_character()))  %>%
  rename(ps = `Phi statistic`) %>%
  # mutate_if(is.numeric, format, digits = 3) %>%
  mutate(ps = signif(as.numeric(ps), digits = 3)) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(P > 0.05 ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi$ statistic` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  rename(`*P*` = P) %>%
  select(c(1:4, 6, 5)) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(0.8, 0.15, 0.15, 0.35, 0.5, 0.15)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>% 
  huxtable::set_number_format(huxtable::everywhere, 2, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 6, 3) %>%
  huxtable::set_number_format(huxtable::everywhere, 5, 4) %>%
  huxtable::print_md(max_width = 80)
```

>>>>

```{r table4, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
read_csv("../../results/tables/AMOVA-year.csv", 
         na = "NA", # spaces read in as spaces
         col_types = cols(.default = col_character()))  %>%
  rename(ps = `Phi statistic`) %>%
  select(-Sigma) %>%
  # mutate_if(is.numeric, format, digits = 3) %>%
  mutate(ps = signif(as.numeric(ps), digits = 3)) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(P > 0.05 ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi$ statistic` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  rename(`*P*` = P) %>%
  select(c(1:4, 6, 5)) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(0.8, 0.15, 0.15, 0.35, 0.5, 0.15)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>% 
  huxtable::set_number_format(huxtable::everywhere, 2, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 6, 3) %>%
  huxtable::set_number_format(huxtable::everywhere, 5, 4) %>%
  huxtable::print_md(max_width = 80)
```
